Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-05-05 exp1/iswc2013.tex
minor corrections
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@508 43ef1190-90fd-4dd7-a769-d0121f02b80e

The experimentation is implemented in R\todo{ref}, which is a free
software environment for statistical computing and graphics. Necessary
tools for DoE has been implemented by the R community in packages
called DoE.base, BsMD and FrF2. The experiments are run on a third
computer in a 1 gigabit LAN with the two experiment hosts.  As
response variable, we have chosen to use the time from the namespace
server lookup to the data has been transferred. This choice is
somewhat arbitrary, many other response variables could be chosen, and
indeed, future work should explore multi-variable responses, but for
simplicity, we think this reflects the total amount of work done by
the SPARQL endpoint well. For the measurements, we have chosen to use
the RCurl package, which is a thin wrapper around the curl
library. Curl has well developed facilities for timing requests and
responses, and so we rely on its measurements.

>>>>

The experimentation is implemented in R\todo{ref}, which is a free
software environment for statistical computing and graphics. Necessary
tools for DoE has been implemented by the R community in packages
called DoE.base, BsMD and FrF2. The experiments are run on a third
computer in a 1 gigabit Ethernet LAN with the two experiment hosts.  As
response variable, we have chosen to use the time from the namespace
server lookup finishes to the data has been transferred. This choice is
somewhat arbitrary, many other response variables could be chosen, and
indeed, future work should explore multi-variable responses, but for
simplicity, we think this reflects the total amount of work done by
the SPARQL endpoint well. For the measurements, we have chosen to use
the RCurl package, which is a thin wrapper around the curl
library. Curl has well developed facilities for timing requests and
responses, and so we rely on its measurements.
